### 2020-08-26 thesis/thesis.tex
[thesis] Missing quotation marks in NFA coexample

\begin{verbatim}
    cohandle Automata using 0 at
        let _ <- observe NFA a in
        let _ <- observe NFA b in
        let _ <- observe NFA b in
        observe NFA a
    through {
        NFA p r ->
            let state <- return fst p in
            let letter <- return snd p in
            <code transitions here> |
        return x -> return x
    }
\end{verbatim}

>>>>

\begin{verbatim}
    cohandle Automata using 0 at
        let _ <- observe NFA "a" in
        let _ <- observe NFA "b" in
        let _ <- observe NFA "b" in
        observe NFA "a"
    through {
        NFA p r ->
            let state <- return fst p in
            let letter <- return snd p in
            <code transitions here> |
        return x -> return x
    }
\end{verbatim}
